---
title: "ABC Segmentation Report (Beta Version)"
author: "CCDS Publicshed: June 30, 2015"
date: 'NATIONAL - ALL PRODUCTS'
output: pdf_document
---
install.packages("alluvial")

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
# Setup working directory
#setwd("C:\\Works\\Francis R Repository\\R_ABC_ALL")

library(tidyr)
library(plyr)
library(dplyr)
library(lubridate)

library(ggplot2)
library(alluvial)
library(scales)
library(grid)

library(knitr)

source("R\\Load.R")
source("C:\\Works\\Francis R Repository\\R_ABC_ALL\\R\\Make_abc.R")
```

##Executive Summary

According to the TMS of 2014, the sales value of Anhui province was 2,052,875 thousand (CNY). The total sales and growth rate of A, B, C segments in 2014 was 1,641,911, 308,283, 102,680 thousand (CNY) and 14.4%, 14.5% and 14.4% respectively. 

##1. Province Segmentation Review
```{r fig.width=10, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE}
source("C:\\Works\\Francis R Repository\\R_ABC_ALL\\R\\Province Segment.R")
```

According to the TMS of 2014, the sales value of Anhui province was 2,052,875 thousand (CNY). The total sales and growth rate of A, B, C segments in 2014 was 1,641,911, 308,283, 102,680 thousand (CNY) and 14.4%, 14.5% and 14.4% respectively. 

##2. Terminal Segmentation Review

Dive into the terminal level, the ABC segment result of 2012 to 2014 is shown as below. In 2014, there were 665 terminals lie into A segment and the proportion was 1.9% by # of terminal:

```{r echo=FALSE, warning=FALSE, message=FALSE}
source("C:\\Works\\Francis R Repository\\R_ABC_ALL\\R\\Terminal Segment.R")
```
`r kable(recid_abcAB, caption="Number of Terminal by ABC Segments", align="r")`

From the perspective of terminal type, Hospital terminal took 34% share by # of terminal. The segment A terminals in hospital part took 4% and in retail part took 0% by # of terminal respectively.

```{r fig.width=10, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE}
print(mekko1)
```

From perspective of terminal type, Hospital terminal took 80% share by sales value. The segment A terminals in hospital part took 83% and in retail part took 66% by sales value.

```{r fig.width=10, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE}
print(mekko2)
```

The sales performance of ABC segments in 2014 is tabulated as below:


`r kable(ptmssubSum, caption="Sales Performence by ABC Segments", align="r")`


The terminal segments progress from 2012 to 2014 at terminal level (In # of terminals) shown as below:

```{r fig.width=10, fig.height=7, echo=FALSE, warning=FALSE, message=FALSE}
source("C:\\Works\\Francis R Repository\\R_ABC_ALL\\R\\Alluvial.R")
```

##3. About ABC Segment Method

About ABC Segment Method, based on Pareto Principle, the portion of the distribution having a large number of contribution far from the "head" or central part of the distribution. Specific to ABC Segment Method, Segment A contributes 80% sales, Segment B contributes 15% and Segment C just contributes the rest of 5%. So when making decisions, we should pay more attention to Segment A, less to B and nothing to C.